Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2016-11-02 ms_pre_post.Rmd
Minor tweaks

<!--- What is 'quantitative theory'? I don't think that I understand what the implied knowledge gap is here, actually. We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model? The hypothesis testing sort of relates to the brief verbal theory that we mention in the introduction, but this manuscript does not address any theoretical knowledge gap using modelling. I don't think this is an esoteric issue; we have to make it clear that we know what we're doing and why we're doing it. Hence, I think that we need to be clear that we are addressing an empirical knowledge gap derived from verbal theory -- or reframe the key questions. --->

@@

<!--- ‘Hypothesis that polyandry and pre- and post-cop IA might co-evolve. However no theory tests these hypotheses or predicts circumstances under which different strategies of pre- and/or post-cop IA might arise and hence drive polyandry evolution, impeding rationalization of empirical observations... --->

>>>>

<!--- I don't think that I understand what the implied knowledge gap is here, actually. We set up an empirical system to test some interesting hypotheses; I suppose that the knowledge gap is whether or not those specific hypotheses are supported given the parameters we model? The hypothesis testing sort of relates to the brief verbal theory that we mention in the introduction, but this manuscript does not address any theoretical knowledge gap using modelling. I don't think this is an esoteric issue; we have to make it clear that we know what we're doing and why we're doing it. Hence, I think that we need to be clear that we are addressing an empirical knowledge gap derived from verbal theory -- or reframe the key questions. --->

@@

<!--- 'Hypothesis that polyandry and pre- and post-cop IA might co-evolve. However no theory tests these hypotheses or predicts circumstances under which different strategies of pre- and/or post-cop IA might arise and hence drive polyandry evolution, impeding rationalization of empirical observations... --->
